\begin{thebibliography}{9}

    \bibitem{KSL15}
        Karen Rose, Scott Eldridge, and Lyman Chapin.
        \textit{The Internet of Things: An Overview}.
        The Internet Society,
        2015.
        URL: \url{https://www.internetsociety.org/resources/doc/2015/iot-overview},
        Accessed June 12, 2019.

    \bibitem{BEK14}
        C. Bormann, M. Ersue, and A. Keranen,
        \textit{“Terminology for constrained node networks,” RFC 7228 (Informational)}.
        Internet Engineering Task Force,
        May 2014.
        URL: \url{http://www.ietf.org/rfc/rfc7228.txt},
        Accessed June 12, 2019.

    \bibitem{White11}
        Elecia White,
        \textit{Making Embedded Systems: Design Patterns for Great Software}.
        O'Reilly Media, 
        2011.

    \bibitem{Thingy19}
        Nordic Semiconductor,
        \textit{Nordic Thingy:52, IoT Sensor Kit} [Online].
        URL: \url{https://www.nordicsemi.com/Software-and-Tools/Development-Kits/Nordic-Thingy-52},
        Accessed June 12, 2019.

    % 5
    \bibitem{TCAD14}
        Kevin Townsend, Carles Cufí, Akiba, and Robert Davidson,
        \textit{Getting Started with Bluetooth Low Energy: Tools and Techniques for Low-Power Networking}.
        O'Reilly Media, 
        2014.

    \bibitem{Ble19}
        Bluetooth SIG,
        \textit{Bluetooth Core Specification v5.1}.
        2019.
        URL: \url{https://www.bluetooth.com/specifications/adopted-specifications},
        Accessed June 13, 2019.

    \bibitem{nrf19}
        Nordic Semiconductor,
        \textit{nRF52840 SoC} [Online].
        URL: \url{https://www.nordicsemi.com/Products/Low-power-short-range-wireless/nRF52840},
        Accessed June 16, 2019.

    \bibitem{zep19}
        \textit{Zephyr Project} [Online].
        URL: \url{https://www.zephyrproject.org/},
        Accessed June 16, 2019.

    \bibitem{ben18}
        Benjamin Bucklin Brown,
        \textit{Over-the-Air (OTA) Updates in Embedded Microcontroller 
            Applications: Design Trade-Offs and Lessons Learned}.
        Analog Dialogue 52, 
        November 11, 2018.     
        URL: \url{https://www.analog.com/media/en/analog-dialogue/volume-52/number-4/over-the-air-ota-updates-in-embedded-microcontroller-applications.pdf},
    
    % 10
    \bibitem{zig14}
        ZigBee Alliance,
        \textit{ZigBee Over-the-Air Upgrading Cluster5, Revision 236,Version 1.1}.
        March 12, 2014.     
        URL: \url{https://www.zigbee.org/wp-content/uploads/2014/11/docs-09-5264-23-00zi-zigbee-ota-upgrade-cluster-specification.pdf},

    \bibitem{dfu19}
        \textit{Device Firmware Update process} [Online].
        URL: \url{https://infocenter.nordicsemi.com/topic/com.nordic.infocenter.sdk5.v15.3.0/lib_bootloader_dfu_process.html},
        Accessed September 7, 2019.
        
\end{thebibliography}